IOI-Offset Analysis for Non-Expressive performances (OFFSET)

### 2020-05-06 material/analysis/stim_n/duration.Rmd
export info about valid performance
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Non-Expressive performances (DURATION)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (duration).

@@

#### Sequence plot
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]
# save data.table for comparison with stim_a
fwrite(duration_seq, file = "./seq.csv")

@@

>>>>

---
title: 'Duration - Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance (duration) from teaching-v2.0.

@@

#### Sequence plot
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

@@

```{r export, include = FALSE}
fwrite(excluded_cv, "./duration_valid.csv")
```

### 2020-05-06 material/analysis/stim_n/ioi_offset.Rmd
export info about valid performance
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Non-Expressive performances (OFFSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (offsets).

@@

>>>>

---
title: 'IOI-Offset Analysis for Non-Expressive performances (OFFSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance (IOI-offset) from teaching-v2.0.

@@

```{r export, include = FALSE}
fwrite(excluded_cv, "./offset_valid.csv")
```
